---
title: "Worksheet_Cartoja#3b"
author: "Jhona Mae Cartoja"
date: "2022-11-21"
output: pdf_document
---

#1. Create a data frame using the table below.
#a. Write the codes.

```{r, error = TRUE}
Respondents <- c(seq(1,20))
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
FathersOccupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
Personsathome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6) 
Siblingsatschool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
Typesofhouses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)

dataframe <- data.frame(Respondents,Sex,FathersOccupation,Personsathome,Siblingsatschool,Typesofhouses)
```



#b.Describe the data. Get the structure or the summary of the data

```{r, error = TRUE}
summary(dataframe)
```
 
 
 
#c. Is the mean number of siblings attending is 5?

Ans: No



#d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.

```{r, error = TRUE}
A1 <- subset(dataframe[1:2, 1:6, drop = FALSE])
A1
```



#e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its
#result.

```{r, error = TRUE}
A2 <- subset(dataframe[c(3,5),c(2,4)])
A2
```



#f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.

```{r, error = TRUE}
A3 <- subset(dataframe[c(1:20), c(2,6)])
type_houses <- A3
```



#g. Select only all Males respondent that their father occupation was farmer. Write
the codes and its output.

```{r, error = TRUE}
A4 <- subset(dataframe[c(1:20), c(2,3)])
Males <- A4[dataframe$FathersOccupation == '1',]
Males
```



#h. Select only all females respondent that have greater than or equal to 5 number
#of siblings attending school. Write the codes and its outputs

```{r, error = TRUE}
A5 <- subset(dataframe[c(1:20), c(2,5)])
females <- A5[dataframe$Siblingsatschool == '1',]
females
```



#2. Write a R program to create an empty data frame. Using the following codes:

```{r, error = TRUE}
dataframe = data.frame(Integers=integer(),
                Doubles=double(), 
                Characters=character(),
                Logicals=logical(),
                Factors=factor(),
                stringsAsFactors=FALSE)

          print("Structure of the empty dataframe:")
          print(str(dataframe))
```
