---
title: "Worksheet#7"
author: "Jhona Mae Cartoja"
date: "2022-12-17"
output: html_document
---

#Basic Statistics
```{r, error=TRUE}
install.packages("Hmisc")
install.packages("pastecs")
```

#1. Create a data frame for the table below 
```{r, error=TRUE}
Student <- seq(1:10)
PreTest <- c(55,54,47,57,51,61,57,54,63,58)
PostTest <- c(61,60,56,63,56,63,59,56,62,61)

dataA <- data.frame(Student,PreTest,PostTest)
dataA
```

#a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
#Write the codes and its result.
```{r, error=TRUE}
library(Hmisc)
library(pastecs)

A <- describe(dataA)

A <- stat.desc(dataA)
```

#2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. 
#For some analyses, it might be useful to convertthe fertilizer levels to an ordered factor.

#a. Write the codes and describe the result.
```{r, error=TRUE}
fertilizers <- c(10,10,10,20,20,50,10,
                20,10,50,20,50,20,10)
fertilizers

data <- factor(fertilizers)
data
```

#3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study
#the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” ,
#“l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense
```{r, error=TRUE}
Subs <- c("l","n","n","i","l","l","n","n","i","l")
Subs
```

#a. What is the best way to represent this in R?
#Answer: By factor
```{r, error=TRUE}
data <- factor(Subs)
data
```

```{r, error=TRUE}
data1 = levels(data) =c("none","light","intense")
data1
```

#4. Sample of 30 tax accountants from all the states and territories of Australia and
#their individual state of origin is specified by a character vector of state mnemonicsas:
```{r, error=TRUE}  
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
             "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
             "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
             "vic", "vic", "act")
state
```

#a. Apply the factor function and factor level. Describe the results.

#Answer:  categorize the data and display the factor's values
```{r, error=TRUE}
data_state <- factor(state)
data_state
```

```{r, error=TRUE}
levels(data_state)
```

#5. From #4 - continuation:

#Suppose we have the incomes of the same tax accountants in another vector (in
#suitably large units of money)
```{r, error=TRUE}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
              62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
              65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
incomes
```

#a. Calculate the sample mean income for each state we can now use the special
#function tapply():
```{r, error=TRUE}
incomes_means <- tapply(incomes, data_state, mean)
incomes_means
```
#b. Copy the results and interpret.
   act      nsw       nt      qld       sa      tas      vic       wa 
44.50000 57.33333 55.50000 53.60000 55.00000 60.50000 56.00000 52.25000 
#Intepretation: It gives the mean of each group 
```

#6. Calculate the standard errors of the state income means (refer again to number 3)
```{r, error=TRUE}
stdError <- function(x) sqrt(var(x)/length(x))
```
#Note: After this assignment, the standard errors are calculated by:
```{r, error=TRUE}
incster <- tapply(incomes, state, stdError)

stdError <- function(x) sqrt(var(x)/length(x))

incster <- tapply(Subs, data, stdError)
incster
```

#a. What is the standard error? Write the codes.
```{r, error=TRUE}      
incster <- tapply(Subs, data, stdError)
incster
 ```
 
#b. Interpret the result. 
#Interpretation: The result is NA because the data inside the object in #3 is a Character
   
   
#7. Use the titanic dataset.
```{r, error=TRUE}
data("Titanic")

titanic_dataset <- data.frame(Titanic)
titanic_dataset
```

#a. subset the titanic dataset of those who survived and not survived. Show the codes and its result.
```{r, error=TRUE}
Titanicdata<- subset(titanic_dataset, select = "Survived")
Titanicdata
 ``` 

#8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this
#chronological grouping of the data. You can create this dataset in Microsoft Excel.

#a. describe what is the dataset all about.
 #Description:The dataset is all about Breast cancer sample

#b.Import the data from MS Excel. Copy the codes.
```{r, error=TRUE}
getwd()

importData <- read.table("BreastCancer.xlsx-Sheet#1.csv", header = TRUE, sep=",")
importData
```

#c. Compute the descriptive statistics using different packages. Find the #values of:

   # c.1 Standard error of the mean for clump thickness.
   # c.2 Coefficient of variability for Marginal Adhesion.
   # c.3 Number of null values of Bare Nuclei.
   # c.4 Mean and standard deviation for Bland Chromatin
   # c.5 Confidence interval of the mean for Uniformity of Cell Shape


#c.1 Standard error of the mean for clump thickness.
```{r, error=TRUE}
stdError <- function(x) sqrt(var(x)/length(x))
stdError(importData)
```

```{r, error=TRUE}
data1 <-(importData$CL..thickness)
data1
```

```{r, error=TRUE}
data2 <- factor(data1)
data2
```

```{r, error=TRUE}
inc <- tapply(data1, data2, stdError)
inc
```

```{r, error=TRUE}
clump <- mean(data1)
clump
```

#c.2 Coefficient of variability for Marginal Adhesion.
```{r, error=TRUE}
CV <-sapply(importData, function(x) sd(x) / mean(x) * 100)
CV 
```

#c.3 Number of null values of Bare Nuclei.
```{r, error=TRUE}
NV <- (importData$Bare..Nuclei)
NV
```

```{r, error=TRUE}
num <-sum(NV %in% c(NA))
num
```

```{r, error=TRUE}
nn <-is.null(list(NV)) 
nn
```  

#c.4 Mean and standard deviation for Bland Chromatin
```{r, error=TRUE}
ndata <- (importData$Bl..Cromatin)
ndata
```

```{r, error=TRUE}
BldChr <- mean(ndata)
BldChr
```

```{r, error=TRUE}
StdD <- sd(ndata)
StdD
```

#c.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r, error=TRUE}
Calc_Mean <- mean(importData$Cell.Shape)
Calc_Mean
```

#d. How many attributes?
```{r, error=TRUE}
attr<-attributes(importData)
attr
```

#e. Find the percentage of respondents who are malignant. Interpret the #results.
```{r, error=TRUE}
A1 <- (importData$Class)
A1
```

```{r, error=TRUE}
nrw <-nrow(importData)
nrw
```

```{r, error=TRUE}
pp <- sum(c(A1 == "malignant")/nrw*100)
pp
```

#9. Export the data abalone to the Microsoft excel file. Copy the codes.
```{r, error=TRUE}
install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")
```

```{r, error=TRUE}
data(abalone)
data(abalone)
View(abalone)
head(abalone)
summary(abalone)
```

#Export Data abalone to xlsx
```{r, error=TRUE}
install.packages("readxl")
install.packages("xlsxjars")
install.packages("xlsx")
```

```{r, error=TRUE}
library(readxl)
library(xlsx)
write.xlsx(abalone,"Abalone.xlsx")
```

