---
title: "RWorksheet_Cartoja#6"
author: "Jhona Mae Cartoja"
date: "2022-11-25"
output: pdf_document
---


```{r, error = TRUE}
library(ggplot2)
library(dplyr)

data(mpg)

dataframe <- as.data.frame(mpg)
dataframe
```

#1. How many columns are in mpg dataset? How about the number of rows? Show the codes and its result.
```{r, error = TRUE}
mpg_dataset <- glimpse(dataframe)

#Answer: It has 11 columns and a row of 234
```

#2. Which manufacturer has the most models in this data set? Which model has the most variations?
```{r, error = TRUE} 
manufacturer <- mpg_dataset %>% group_by(manufacturer,model) %>% count()
manufacturer
```

#a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r, error = TRUE}
unique_model <- mpg_dataset %>% group_by(manufacturer) %>%
            distinct(model) %>% count()
unique_model

colnames(unique_model)<-c("manufacturer", "Unique Counts")
```

#b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r, error = TRUE}
plot(manufacturer)

ggplot(manufacturer, aes(manufacturer, model)) + geom_point()
```

#3. Same dataset will be used. You are going to show the relationship of the model and the manufacturer.

#a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r, error = TRUE}
 # Answer: It shows the point graph of a model and manufacturer of mpg data set.

ggplot(dataframe, aes(model, manufacturer)) + geom_point()
```

#b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r, error = TRUE}
#Answer: For me, basically, it is useful. But it can be more modify if there is a legend to help reading the data easily.
```

#4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.
```{r, error = TRUE}
cars_per_model <- mpg_dataset %>% group_by(model) %>% count()
cars_per_model

colnames(cars_per_model) <- c("Model","Counts")
cars_per_model
```

#a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r, error = TRUE}
qplot(model, data = dataframe,
      main = "Number of Cars per Model",
      xlab = "Model",
      ylab = "Number of Cars", geom = "bar", fill = manufacturer) + coord_flip()
```

#b. Use only the top 20 observations. Show code and results.
```{r, error = TRUE}
twenty <- cars_per_model[1:20,] %>% top_n(2)
twenty

ggplot(twenty, aes(x = Model, y = Counts)) + geom_bar(stat = "Identity") + coord_flip()
```

#5. Plot the relationship between cyl - number of cylinders and displ- engine displacement using geom_point with aesthetic colour = engine displacement.  
#Title should be “Relationship between No. of Cylinders and Engine Displacement”.
```{r, error = TRUE}
ggplot(data = mpg_dataset, mapping = aes(x = displ, y = cyl, main = "Relationship between No of Cylinders
          and Engine Displacement")) +
geom_point(mapping = aes(colour = "engine displacement"))
```

#b. How would you describe its relationship?
  #Answer: The cyl is in the y axis and the disp is in the x axis and can easily read the clustered data of which indicates the engine displacement.

#6. Get the total number of observations for drv - type of drive train
#(f = front-wheel drive,r = rear wheel drive, 4 = 4wd) and class - type of class
#(Example: suv, 2seater, etc.). Plot using the geom_tile() where the number of observations for 
#class be used as a fill for aesthetics.

#a. Show the codes and its result for the narrative in #6.
```{r, error = TRUE}
ggplot(data = mpg_dataset, mapping = aes(x = drv, y = class)) +
geom_tile(aes(fill = class))
```

#b. Interpret the result.
```{r, error = TRUE}
#Answer: The y aixs is class and the x axis is drv. It graph and show the data. Specifically the data are on  different colors.
```

#7. Discuss the difference between these codes. Its outputs for each are shown below.
```{r, error = TRUE}
#Answer:The two code are the same. In the code it says that the colour is both 
#blue but on the first code the result is color red and on the smaller graph. 
#Unlike on the second code that the graph is much more larger than the first graph and the 3result is on color blue.

ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))


ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```

#8. Try to run the command ?mpg. What is the result of this command?
```{r, error = TRUE}  
command <-? mpg
command


   #Answer: The result of the code is the description or the data set of mpg.
```

#a. Which variables from mpg dataset are categorical?
```{r, error = TRUE}
   #Answer: The Manufacturer, Model, Trans, drv, fl, class, cyl, cty, and hwy.
```

#b. Which are continuous variables?
```{r, error = TRUE}
   #Answer: displ, year, cyl, cty, and hwy.
```

#c. Plot the relationship between displ (engine displacement) and hwy(highway miles
#per gallon). Mapped it with a continuous variable you have identified in #5-b.What is its result? Why it produced such output?
```{r, error = TRUE}  
  #Answer: The result was graph and it shows that they are in the positive rate.
 
ggplot(mpg, aes(x = cty, y = hwy, colour = displ)) + geom_point()
```

#9. Plot the relationship between displ (engine displacement) and hwy(highway miles 
#per gallon) using geom_point(). Add a trend line over the existing plot usinggeom_smooth() 
#with se = FALSE. Default method is “loess”.
```{r, error = TRUE} 
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping = aes(color = class)) +
  geom_smooth(se = FALSE)
```

#10. Using the relationship of displ and hwy, add a trend line over existing plot.
#Set the se = FALSE to remove the confidence interval and method = lm to check for linear modeling.
```{r, error = TRUE} 
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point()+
  geom_smooth(se = FALSE, method = lm)
```

