---
title: "RWorksheet_Cartoja#4"
author: "Jhona Mae Cartoja"
date: "2022-11-22"
output: pdf_document
---

#1. The table below shows the data about shoe size and height. Create a data frame..
#a. Describe the data.
```{r, error = TRUE}
Shoesize <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,
              13.0,7.5,10.5,8.5,12.0,10.5,
              13.0,11.5,8.5,5.0,10.0,
              6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)

Height <- c(66.0,68.0,64.5,65.0,70.0,
            64.0,70.0,71.0,72.0,64.0,
            74.5,67.0,71.0,71.0,77.0,72.0,
            59.0,62.0,72.0,66.0,64.0,67.0,73.0,
            69.0,72.0,70.0,69.0,70)

Gender <- c("F","F","F","F","M","F","M","F","M",
            "M","M","F","M","M","M","M","F","F",
            "M","F","M","M","M","F","M","M","M","M")

dataframe <- data.frame(Shoesize,Height,Gender)
dataframe
```

#b. Find the mean of shoe size and height of the respondents. Copy the codes and results.

```{r, error = TRUE}
summary(dataframe)
```

#c. Is there a relationship between shoe size and height? Why?

# -Yes, there is. Sometimes, your shoe size varies on your height. The higher the height, the greater the shoe size.


#2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.Consider data consisting of the names of months:

```{r, error = TRUE}
months <- c("March","April","January","November","January",
            "September","October","September","November",
            "August","January","November","November","February",
            "May","August", "July","December","August","August",
            "September","November","February","April")

factor_months <- factor(months)
factor_months
```


#3. Then check the summary() of the months_vector and factor_months_vector.Interpret the results of both vectors. Are they both equally useful in this case?
```{r, error = TRUE}
summary(months)
summary(factor_months)
```
#4. Create a vector and factor for the table below.
```{r, error = TRUE}
factor_data <- c(1,4,3)

new_order_data <-factor(factor_data,levels=c("East","West","North"))

print(new_order_data)
```

#5. Enter the data below in Excel with file name = import_march.csv

#a. Import the excel file into the Environment Pane using read.table() function.
```{r, error = TRUE}
data_tab <- read.table("/cloud/project/import_march.csv", header=TRUE, sep = ",")
data_tab
```

#b. View the dataset. Write the code and its result.
```{r, error = TRUE}
data_tab <- read.csv("/cloud/project/import_march.csv")
data_tab
```